Eco-evolutionary dynamics of finite populations from first principles

### 2023-03-26 ind_files/02_math_background.tex
Add footnote on limit in L^2 vs pointwise limit

The second integral in equation \eqref{ito_SDE_integral} is It\^o's `stochastic integral', and is to be interpreted in the following sense: Fix a time $T > 0$. For any $n\geq2$, let $\Pi_n = \{t_1,t_2,\ldots,t_n\}$ be a partition of the interval $[0,T]$. In other words, $\Pi_n$ divides $[0,T]$ into $n$ slices of the form $[t_i,t_{i+1}]$ such that $0 = t_0 < t_1 < t_2 < \ldots < t_n = T$. Then, the (It\^o) stochastic integral from $0$ to $T$ can be thought of as:
\begin{equation*}
\int\limits_{0}^{T} G(s,X_s)dW_s \coloneqq \lim_{n \to \infty} \sum\limits_{t_i \in \Pi_n}G(t_i,X_{t_i})(W_{t_{i+1}}-W_{t_i})  
\end{equation*}
That is to say, it is obtained by making successively finer slices of the form $[t_i,t_{i+1}]$, and then computing the `area of the rectangle' formed with $W_{t_{i+1}}-W_{t_i}$ and $G(t_i,X_{t_i})$ as sides. This should look similar to the classic Riemann integral, with the uniform width $t_{i+1}-t_i$ of the Riemann integral replaced by a random width corresponding to the random displacement of a Brownian particle during the uniform time interval $[t_i,t_{i+1}]$.

Equation \eqref{ito_SDE_integral} is often represented in the compact `differential' form:

@@

The physics literature also often uses the `Langevin form':

>>>>

The second integral in equation \eqref{ito_SDE_integral} is It\^o's `stochastic integral', and is to be interpreted in the following sense: Fix a time $T > 0$. For any $n\geq2$, let $\Pi_n = \{t_1,t_2,\ldots,t_n\}$ be a partition of the interval $[0,T]$. In other words, $\Pi_n$ divides $[0,T]$ into $n$ slices of the form $[t_i,t_{i+1}]$ such that $0 = t_0 < t_1 < t_2 < \ldots < t_n = T$. Then, the (It\^o) stochastic integral from $0$ to $T$ can be thought of as:
\int\limits_{0}^{T} G(s,X_s)dW_s \coloneqq \lim_{n \to \infty} \sum\limits_{t_i \in \Pi_n}G(t_i,X_{t_i})(W_{t_{i+1}}-W_{t_i})  
That is to say, it is obtained by dividing our time interal into slices of the form $[t_i,t_{i+1}]$, computing the `area of the rectangle' formed with $W_{t_{i+1}}-W_{t_i}$ and $G(t_i,X_{t_i})$ as sides, and then taking the limit\footnote{If you know a little bit of mathematics, it bears noting that this limit is in $L^2(\mathbb{P})$, whereas the corresponding limit in the usual Riemann-Stieltjes integral is evaluated pointwise. If you don't know what this sentence means, just ignore it for the purposes of this thesis :)} of finer and finer slices of time. This should look similar to the classic Riemann integral, with the uniform width $t_{i+1}-t_i$ of the Riemann integral replaced by a random width $W_{t_{i+1}}-W_{t_i}$ corresponding to the (random) displacement of a Brownian particle during the uniform time interval $[t_i,t_{i+1}]$.\\
Equation \eqref{ito_SDE_integral} is often represented in the `differential' form:

@@

The physics literature also often uses the `Langevin' form:
